---
title: "tutorialgap"
output: html_document
---

#I began by creating a rmd file that contains the code that I want to run. First, I loaded the packages that are needed. 

```{r,eval=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)

```

##Next I read in the gapminder data from online. 

```{r,eval=FALSE}
gap <- read.csv(url("https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/gh-pages/_episodes_rmd/data/gapminder-FiveYearData.csv"))

```

##After that I thought about the best way to represent this data. We wanted to look at life expectancy over time for each country. There aren't any coordinates, so a map would be hard to make. I chose to make a dot plot for each country since it would be easy. Heres the code: 

```{r}
for (var in unique(gap$country)) {
  print( ggplot(gap[gap$country==var,], aes(year, lifeExp)) + geom_point() + ggtitle(var) )
}

```


##This is where I would put my make file if I had one. First you make the file by going file > new file > text file. Then you name it Makefile and fill it with stuff.  I think the idea is to make the rmd file render a pdf somehow. Here is what I attempted: 

```{r,eval=FALSE}
report.pdf: gap.Rmd
	Rscript -e 'rmarkdown::render("$<")'
```

Other Makefiles were more complicated than this so I am not sure if what I have means anything. 