---
title: "R programming (r4ds Section III)"
author: "name"
date: "date"
output: 
  html_document: 
    keep_md: yes
---

# Ch 18: Pipes

_Demonstrate the use of the regular pipe (`%>%`) and the "explosion" operator (`%$%`) in some example_

```{r}
library(magrittr)
nums = c(1,2,3,4,5,6,7,8,9) %>% matrix(ncol = 3) %>% data.frame()

wtb = nums %$% table(X1,X2,X3)
```


----

# Ch 19: Functions

### 19.2: When should you write a function?
Answer any 3
```{r}
rescale01 <- function(x) {
  rng <- range(x, na.rm = TRUE)
  (x - rng[1]) / (rng[2] - rng[1])
}
rescale01(c(0, 5, 10))
rescale01(c(1, 2, 3, NA, 5))
```
1. If na.rm = FALSE, then all the max's and mins become na. 

3. 
```{r}
meanfun = function(x){
  c(mean(is.na(x)))
}

anotherfun = function(x){
  c(x / sum(x, na.rm = TRUE))
}

sdmean = function(x){
  c(sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE))
}
```

6. 
```{r}
setwd("C:/Users/mitch2/Documents/School/499/assignments-mborgert")
is_directory <- function(x) file.info(x)$isdir
```
This tells you whether a file is a directory.

```{r}
is_readable <- function(x) file.access(x, 4) == 0
?file.access
```
This is a function to test if a file is readable.

_Describe one time where you wish you had written a function, but didn't._
For a project in Math 458. It took way too much copying and pasting. 


### 19.3: Functions are for humans and computers

1.
```{r}
contains_prefix <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}

contains_prefix("prefix","pre")
```
This says if a prefix is in a word. 

```{r}
final_number_remover <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}

final_number_remover(c(1,2,3,4))
```
This removes the final number in a vector, if there is 1 number or less it returns null.

```{r}
f3 <- function(x, y) {
  rep(y, length.out = length(x))
}

f3(555,"dootfsdfs")
?rep
```




_What does "Functions are for humans and computers" mean to you?_

### 19.4 Conditional execution
Answer any 3
1. 
```{r}
?ifelse
x = c(6:-4)
sqrt(x)
sqrt(ifelse(x >= 0, x, NA))

```
```{r}
x = 11
if(x == 11){
  x = x + 1
}
```

ifelse does the else in the function. 

3. 
```{r}
fizzbuzz.fun = function(x){
if(x %% 3 == 0 && x %% 5 == 0) {
  c("fizzbuzz")
}
else if(x %% 3 == 0){
  c("fizz")
}
else if(x %% 5 == 0){
  c("buzz")
}
}

fizzbuzz.fun(45)
```

6. 
```{r}
x = "e"
switch(x, 
  a = ,
  b = "ab",
  c = ,
  d = "cd"
)

```
Nothing happens if x = "e". Switch switches stuff. 
```{r}
switch(1,"red","green","blue")
switch(2,"red","green","blue")

centre <- function(x, type) {
 switch(type,
        mean = mean(x),
      median = median(x),
         trimmed = mean(x, trim = .1))
}
x = rnorm(10)
centre(x,"mean")

```

### 19.5 Function arguments

2. Trim chops off an amount of decimals. You use it when you want less decimals. 

4.
```{r}
?cor
```
Pearson is default. The three are different types of computing the correlation. 

### 19.6: Return values
_Is it mandatory that you `return()` a value from a function? If not, give on reasons for why you would want to do so. If so, explain what happens if you don't include the return._

It's not necessary to return someone, the function still runs. 

### 19.7: Environment
_What's the problem with the example function at the beginning of this chapter?_

Y wasn't initialized. 

----

# 20: Vectors

###  20.3: Important types of atomic vector

```{r}
library(dplyr)
near
```
if x-y is less than some total, they are near. 

5. the parse atomic functions let you turn a string into others. 

### 20.4: Using Atomic Vectors




### 20.5: Recursive vectors (lists)
I drew the lists. 

### 20.7: Augmented vectors

_Describe at least two differences between a `data.frame` and a `tibble`_

All elements must be vectors. All elements must be the same length. 
----

# Chapter 21: Iteration

### 21.2: For Loops
Any one question

### 21.3: For Loop Variations
create a list with each dataframe as an entry then data.frame( each entry in the list )

### 21.4: For loops vs functionals
```{r}
col_summary <- function(df, fun) {
  out <- vector("double", length(df))
  for (i in seq_along(df)) {
    if(is.numeric(df[[i]]) == TRUE){
    out[i] <- fun(df[[i]])
    }
    else{
      out[i] <- NA
    }
  }
  out
}
```


### 21.5: the map function
2. make a list that has as many columns as a dataframe. for loop through the colums and fill the list the is.factor results. 

```{r}
library(purrr)
map(-2:2, rnorm, n = 5)
map_dbl(-2:2, rnorm, n = 5)
?map_dbl
```
The first creates 5x5 rnorm numbers. The second does not work because 


----

End here. The rest of 21 is for your info only

